\textbf{Designing a Virtual Security Layer for Cloud Content}

### 2016-01-25 tex/paper.tex
Added full copy and JPF introduction

\section{Model}
The model for this work should show how the data can not be accessed or modified by unauthorized
users and how the integrity of the data is always kept in the Perius system.

@@

\begin{itemize}
    \item if a user wants to update a file in a content, the file is copied and the original is intact
    \item if a user reads content and then writes to it, the content is directly changed
    \item if a user copies content, a new content is created at the destination with reference to the same
          file
    \item if a user reads from a container and then writes to it, the container is directly changed
          (Which means last write wins, which doesn't matter)
    \item if a user copies a container, the full container tree is re created with new ids at the destination,
          its content still refers to the same files.
\end{itemize}

@@

\subsubsection{Full Copy}
\fix Maybe a short description of full copy, as opposed to copy-on-write

@@

As can be seen several expected endpoints are missing, this is intentional as the operations missing
can be performed in a more efficient way. Such endpoint is for example $GET
projects/\{id\}/containers$ as all containers exist in $GET projects/\{id\}$ and the interface
should present a file structure where both content and containers are shown.

@@

\subsubsection{Security of the system}
\paragraph{Authorization}
\paragraph{Audit logs}

\section{JPF}
\fix Not sure where to put this section or if it's even relevant any more, maybe skip JPF and put
the entities under implementation -> design
\subsection{Entities}
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{High Level Entity Relationships}
    \label{fig:relation}
\end{figure}

@@

\subsection{Future work}

>>>>

\label{sec:model}
\section{Model}
The model for this work should show how the data can not be accessed or modified by unauthorized
users and how the integrity of the data is always kept in the Perius system.

@@

\begin{itemize}
    \item if a user wants to update a file in a content, the file is copied and the original is intact
    \item if a user reads content and then writes to it, the content is directly changed
    \item if a user copies content, a new content is created at the destination with reference to the same
          file
    \item if a user reads from a container and then writes to it, the container is directly changed
          (Which means last write wins, which doesn't matter)
    \item if a user creates a snapshot of a container, the full container tree is re created with 
          new ids at the destination, its content still refers to the same files.
\end{itemize}

@@

\subsubsection{Full Copy}
Full copy or deep copy, as opposed to copy-on-write, is a copy where everything is copied directly
and not only when an object is changed. This is easier to implement but is in most cases more
inefficient as more disk space will have to be used and if used with for example certain tree 
structures the part of the tree that needs to be copied will have to be traversed.

@@

As can be seen several expected endpoints are missing, this is intentional as the operations missing
can be performed in a more efficient way. Such endpoint is for example \textit{GET 
projects/\{id\}/containers} as all containers exist in \textit{GET projects/\{id\}} and the interface
should present a file structure where both content and containers are shown.

@@

\subsubsection{Security of the system}
\paragraph{Authorization}
The authorization of the system is currently being handled by LDAP

\paragraph{Audit logs}

\section{JPF}
\fix Not sure where to put this section
JPF was used to test the idea and state transitioning of the application. Its a very simplified
version of the real system that still contains all the important Copy-on-Write core concepts and the 
assumptions that have been made for the model. This simplified version could then be automatically
tested for soundness. It is not a proof that the model works, but it is very exhaustive in its
testing.

\subsection{Entities}
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{High Level Entity Relationships}
    \label{fig:relation}
\end{figure}

@@

\subsection{Future work}
Full access control was not implemented according to the model described in ~\ref{sec:model}, it
was only implemented to check whether a user should have access to the system as a whole or not, the
implementation did not set or check any specific access rights to certain contents or containers.
